The paper on blockchain front-running

### 2018-09-25 frontrunning/Latex/sections/paper.tex
[frontrunning] Edits

The mechanics of frontrunning works on all DApps but front-running is not necessarily beneficial, depending on the DApp's internal logic and/or  as any mitigations it might implement. Therefore DApps need to be studied individually or in categories. This paper is a series of case studies of DApps deployed on Ethereum (a popular blockchain supporting DApps) from each category of the top 25 most active.\footnote{List of decentralized applications \url{https://DAppradar.com/DApps}} We do case studies on decentralized exchanges (\eg Bancor), crypto-collectables (\eg CryptoKitties), gambling services (\eg Fomo3D), and decentralized name services (\eg Ethereum Name Service). We also study initial coin offerings (ICOs), which by happenstance, did not appear in the top 25 on our sample day. After a few hacking incidents of high valued smart contracts~\cite{siegel2016daohack}, ICOs started to implement restrictions and capped how much funds can be gathered. This scarcity of the initial coins made for a competition to incentivize big investors to get in and buy the tokens at a discounted price and sell them to latecomers on the open markets~\cite{zetzsche2018ico, li2018initial}. ICOs started to experiment with different fair capping methods, such as reverse dutch auction and dynamic ceilings~\cite{kaal2017initial}. We show empirical evidence of a miner purchasing tokens ahead of other users in Status.im. Finally, proposals to eliminate or mitigate frontrunning from DApps are scattered across forums, proposed standards (called EIPs in Ethereum) and academic papers; we systemize them the last section.

@@

Designing truly decentralized exchanges, where the orderbook is implemented directly on a public blockchain, is being pursued by a number of projects [\textblue{cite github page}]. These designs generally face the following attack (illustrated in Figure~\ref{fig:RegularFrontrunning}). An adversary can monitor the network with a full node for pending \textit{buy} (or \textit{sell}) transactions which could increase (or \textit{decrease}) the future price of the asset. A front-runner can send a competing orders with a higher gas price, and hope to have her transactions mined ahead of the original pending transaction. The benefits of doing this vary. If the original bid is a large market order (\ie it will execute at any price), the adversary can front-run a pair of limit orders that will bid near the best offer price and offer at a higher price. If these execute ahead of the market order, the front-runner profits by scalping the price of the shares. If the adversary has pre-existing offers likely to be reached by the market order, she could front-run a cancelation and a new offer at a higher price. A simpler attack would be to guage the demand for trades at a given price by the number of pending orders, and to front-run at the same price in hopes that the market demand is the result of accurate new market information. Miners are in the best position to conduct these attacks as they hold fine-grained control over the exact set of transactions that will execute and in what order and can mix in their own (late) transactions without broadcasting them. Miners do however have to commit to what their own transactions will be before beginning the proof of work required to solve a block.

@@

During the time the ICO was open for participation, there were reports of Ethereum network being unusable and transactions were not confirming. Further study showed that some mining pools might have been manipulating the network for their own profit. In addition, there were many transactions sent with a higher gas price to front-run other transactions, however, these transactions were failing due to the restriction in the ICO smart contract to reject any transactions with higher than 50 \textit{GWei} gas price (another mitigation against frontrunning).

@@

\subsection{Data Collection and Analysis}
According to analysis we carried out, we discovered that the F2Pool---an Ethereum mining pool that had around 23\% of the mining hash rate at the time (Figure~\ref{fig:mining_pool_ratio})---sent 100 Ether to 30 new Ethereum addresses before the Status.im ICO started. When the token sale opened, F2Pool contsructed 31 transactions to the ICO token sale smart contract from the addresses these new address, without broadcasting these transactions to the network. They used their entire mining power to mine their own transactions and some other potentially failing high gas price transactions.

Ethereum's blockchain contains all transaction ever made on Ethereum. While the default client and online blockchain explorers offer some limited querying, in order to analyze this case, we built our own database. Specifically, we used open source projects such as Go Ethereum implementation\footnote{Official Go implementation\url{https://github.com/ethereum/go-ethereum}} for the full node, a python script for extracting, transforming and loading ethereum blocks, named \texttt{ethereum-etl}~\cite{ethereumetl} and Google BigQuery.\footnote{\url{https://cloud.google.com/bigquery/}} Using this software stack, we were able to isolate transactions within the Status.im ICO sale. We used data analysis tool \texttt{Tableau}.\footnote{\url{https://www.tableau.com/}} A copy of this dataset and the initial findings can be found in our Github repository.\footnote{\url{github.com/} Removed for anonymity.}

@@

\begin{figure}[t]
\centering
\includegraphics[width=0.9\linewidth]{figures/Vulnerable_Loopring.png}
\caption{\scriptsize \emph{submitRing} Transaction in the old version of the Loopring protocol. Any user can regenerate this transaction by replacing the miner's address with his address and signing the hash of the ring using his private key. \label{fig:vulnerable_loopring}}
\end{figure}
%https://www.lucidchart.com/invitations/accept/33d38ce9-4660-4743-806d-45c72f7e8393
\begin{figure}[t]
\centering
\includegraphics[width=0.7\linewidth]{figures/Dual_Authoring_Loopring.png}
\caption{\scriptsize \emph{submitRing} Transaction in the new version of the Loopring protocol. Other users cannnot regenerate this transaction as they do not access auth-keys and hence are not able to create the signatures. \label{fig:not_vulnerable_loopring}}
\end{figure}
%https://www.lucidchart.com/invitations/accept/8dee869c-482c-433f-a901-8d041a1dc526

@@

In the case of decentralized exchanges, users can use commit/reveal for bids, where commitments are placed in an ordered queue and executed in a later round after a reveal. This mitigation seems to require further research. One trader strategy is to flood orders at the commitment stage, but then only selectively and adaptively choose which to reveal. Collateralization is another challenge, where revealed bids may simply be intentions to execute but additional transactions are required to move the money or tokens; a transaction that can also be aborted early. One mitigation to early aborts is having users post a fidelity bond that can be automatically dispensed if they fail to fully execute committed transactions (as used in~\cite{} \textblue{Cite paddy's paper on boardroom voting on ethereum}). Commit/reveal is also seen in on-chain voting~\cite{adChainPLCRVoting}. Using sealed votes, voters can make sure their votes are hidden until a later date, however, their participation and weight of the vote are publicly known.

>>>>

The mechanics of front-running works on all DApps but front-running is not necessarily beneficial, depending on the DApp's internal logic and/or  as any mitigations it might implement. Therefore DApps need to be studied individually or in categories. This paper is a series of case studies of DApps deployed on Ethereum (a popular blockchain supporting DApps) from each category of the top 25 most active.\footnote{List of decentralized applications \url{https://DAppradar.com/DApps}} We do case studies on decentralized exchanges (\eg Bancor), crypto-collectables (\eg CryptoKitties), gambling services (\eg Fomo3D), and decentralized name services (\eg Ethereum Name Service). We also study initial coin offerings (ICOs), which by happenstance, did not appear in the top 25 on our sample day. After a few hacking incidents of high valued smart contracts~\cite{siegel2016daohack}, ICOs started to implement restrictions and capped how much funds can be gathered. This scarcity of the initial coins made for a competition to incentivize big investors to get in and buy the tokens at a discounted price and sell them to latecomers on the open markets~\cite{zetzsche2018ico, li2018initial}. ICOs started to experiment with different fair capping methods, such as reverse dutch auction and dynamic ceilings~\cite{kaal2017initial}. We show empirical evidence of a miner purchasing tokens ahead of other users in Status.im. Finally, proposals to eliminate or mitigate front-running from DApps are scattered across forums, proposed standards (called EIPs in Ethereum) and academic papers; we systemize them the last section.

@@

Designing truly decentralized exchanges, where the order book is implemented directly on a public blockchain, is being pursued by a number of projects [\textblue{cite github page}]. These designs generally face the following attack (illustrated in Figure~\ref{fig:RegularFrontrunning}). An adversary can monitor the network with a full node for pending \textit{buy} (or \textit{sell}) transactions which could increase (or \textit{decrease}) the future price of the asset. A front-runner can send a competing orders with a higher gas price, and hope to have her transactions mined ahead of the original pending transaction. The benefits of doing this vary. If the original bid is a large market order (\ie it will execute at any price), the adversary can front-run a pair of limit orders that will bid near the best offer price and offer at a higher price. If these execute ahead of the market order, the front-runner profits by scalping the price of the shares. If the adversary has pre-existing offers likely to be reached by the market order, she could front-run a cancelation and a new offer at a higher price. A simpler attack would be to gauge the demand for trades at a given price by the number of pending orders, and to front-run at the same price in hopes that the market demand is the result of accurate new market information. Miners are in the best position to conduct these attacks as they hold fine-grained control over the exact set of transactions that will execute and in what order and can mix in their own (late) transactions without broadcasting them. Miners do however have to commit to what their own transactions will be before beginning the proof of work required to solve a block.

@@

During the time the ICO was open for participation, there were reports of Ethereum network being unusable and transactions were not confirming. Further study showed that some mining pools might have been manipulating the network for their own profit. In addition, there were many transactions sent with a higher gas price to front-run other transactions, however, these transactions were failing due to the restriction in the ICO smart contract to reject any transactions with higher than 50 \textit{GWei} gas price (another mitigation against front-running).

@@

\subsection{Data Collection and Analysis}
According to analysis we carried out, we discovered that the F2Pool---an Ethereum mining pool that had around 23\% of the mining hash rate at the time (Figure~\ref{fig:mining_pool_ratio})---sent 100 Ether to 30 new Ethereum addresses before the Status.im ICO started. When the token sale opened, F2Pool constructed 31 transactions to the ICO token sale smart contract from the addresses these new address, without broadcasting these transactions to the network. They used their entire mining power to mine their own transactions and some other potentially failing high gas price transactions.

Ethereum's blockchain contains all transaction ever made on Ethereum. While the default client and online blockchain explorers offer some limited querying, in order to analyze this case, we built our own database. Specifically, we used open source projects such as Go Ethereum implementation\footnote{Official Go implementation\url{https://github.com/ethereum/go-ethereum}} for the full node, a python script for extracting, transforming and loading Ethereum blocks, named \texttt{ethereum-etl}~\cite{ethereumetl} and Google BigQuery.\footnote{\url{https://cloud.google.com/bigquery/}} Using this software stack, we were able to isolate transactions within the Status.im ICO sale. We used data analysis tool \texttt{Tableau}.\footnote{\url{https://www.tableau.com/}} A copy of this dataset and the initial findings can be found in our Github repository.\footnote{\url{github.com/} Removed for anonymity.}

@@

\begin{figure}[t]
\centering
\includegraphics[width=0.9\linewidth]{figures/Vulnerable_Loopring.png}
\caption{\scriptsize \emph{submitRing} Transaction in the old version of the Loopring protocol. Any user can regenerate this transaction by replacing the miner's address with his address and signing the hash of the ring using his private key. \label{fig:vulnerable_loopring}}
\end{figure}
%https://www.lucidchart.com/invitations/accept/33d38ce9-4660-4743-806d-45c72f7e8393
\begin{figure}[t]
\centering
\includegraphics[width=0.7\linewidth]{figures/Dual_Authoring_Loopring.png}
\caption{\scriptsize \emph{submitRing} Transaction in the new version of the Loopring protocol. Other users cannot regenerate this transaction as they do not access auth-keys and hence are not able to create the signatures. \label{fig:not_vulnerable_loopring}}
\end{figure}
%https://www.lucidchart.com/invitations/accept/8dee869c-482c-433f-a901-8d041a1dc526

@@

In the case of decentralized exchanges, users can use commit/reveal for bids, where commitments are placed in an ordered queue and executed in a later round after a reveal. This mitigation seems to require further research. One trader strategy is to flood orders at the commitment stage, but then only selectively and adaptively choose which to reveal. Collateralization is another challenge, where revealed bids may simply be intentions to execute but additional transactions are required to move the money or tokens; a transaction that can also be aborted early. One mitigation to early aborts is having users post a fidelity bond that can be automatically dispensed if they fail to fully execute committed transactions (as used in~\cite{mccorry2017smart}). Commit/reveal is also seen in on-chain voting~\cite{adChainPLCRVoting}. Using sealed votes, voters can make sure their votes are hidden until a later date, however, their participation and weight of the vote are publicly known.
